The Exoplanet Orbit Database 2, 2014 updates

### 2014-03-14 draft/ms.tex
Section 3 and 5 update and random notes for abstract

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Make sure to mention: data are available at exoplanets.org; KOIs are included.
\end{abstract}

@@

\end{itemize}
Some of the exoplanets primarily detected by these methods do not have
well-determined orbital parameters, and thus they are categorized as
``Other Planets'' on exoplanets.org instead of being in the EOD. These
planets can be displayed by check the `Other' option for the EDE
table. As of March 2014, no microlensing or imaging planets are in the
EOD, while several timing exoplanets have well-determined orbital
parameters and are included in the EOD.

ZZZ mention there have been no astrometry planets so far, but we do
plan to include them if any robust detections occur.

@@

ZZZ Any planned future improvements and updates?  I hesitate to
promise here, lest we overpromise.  We do hope to include images of
directly imaged planets (where allowed under copyright law) and
perhaps light curves for transits.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Make sure to mention: data are available at exoplanets.org; KOIs are included.
ZZZ Also mention the number of confirmed planets? and maybe the scope of the EOD (what are in our database)
\end{abstract}

@@

\end{itemize}
Some of the exoplanets primarily detected by these methods do not have
well-determined orbital parameters, and thus they are categorized as
``Other Planets'' on exoplanets.org instead of being in the EOD. These
planets can be displayed by check the `Other' option for the EDE
table. As of March 2014, no microlensing or imaging planets are in the
EOD, while several timing exoplanets have well-determined orbital
parameters and are included in the EOD. Moreover, there have been no astrometry planets in the EOD but we plan to include them if any robust detections occur.

@@

We hope to include images of directly imaged planets (where allowed under copyright law) and
light curves for transits in the future.
